\section{Model-based Attack Generation}

One of the main challenges to solving this problem is how to generate effective test cases (\ie, attacks)
since there is an exponential number of possible test cases.
To overcome this challenge, we devise a model-guided attack generation technique
that focuses on testing only important aspects of the congestion control technique.
The key insights behind our approach are: (i) the model of a congestion control technique
essentially describes how it transitions through different states and
takes appropriate actions to deal with the current network condition
and (ii) the attacker induces the victim to take some actions that are not
appropriate in the current context but favorable for the attacker.
Depending on the attacker's goal (\eg, increase or decrease throughput),
we utilize the user-provided model to find the paths containing
the vulnerable actions that the attacker wants the victim to perform.
These paths provide us some potential abstract test cases, which 
in turn need to be converted to concrete ones before conducting the actual
test using our platform.

\subsection*{Algorithm}

\paragraph{Problem definition} Given a directed \textbf{cyclic} graph (\ie, the model), we need to 
find all paths containing specific edge labels (\ie, actions) starting from the root node.

\paragraph{Background} 
%The characteristics of 
The graph ($G = \langle V, E \rangle$):
\begin{itemize}
  \item
  is a directed graph
  \item
  Contains cycles (makes the problem challenging)
  \item 
  By specific edge label, we mean only the action part of an edge label.
  %In other words, a specific edge label is vulnerable action
  \item 
  One vulnerable action can appear on multiple edges. 
  Formally, a vulnerable action $A$ can appear $(x, y) \in E$ for any $x, y \in V$
\end{itemize}
  

\paragraph{Requirements}  
\begin{itemize}
  \item
  A desired goal of the attacker may require a combination of one or more vulnerable actions to take place. 
  For now, we assume a goal maps to only one vulnerable action.
  \item
  The desired path must contain an edge with the vulnerable action
  \item
  To obtain a path that can generate a test case with repeated attacks, 
  the path must contain a vulnerable action edge as a part of a cycle. 
  The cycle dictates the repetition of the attack.
\end{itemize}

Our algorithm is shown in Algorithm~\ref{algorithm:modelsearch}.

\begin{algorithm} %[!t]
\DontPrintSemicolon
\SetKwProg{Fn}{Function}{}{}
\SetKwFunction{FMain}{Main}
\SetKwFunction{FScan}{Scan}


%\small
 \tcc{{Objective}: Find all paths containing a specific action in a given graph (model)}
 \KwIn{Graph $G = (V,E)$ and action $A$}
 \KwOut{All paths containing $A$ }
 
 \BlankLine 
 \BlankLine
 
 \tcc{
 $adj: (V \times E) \mapsto V$. For example, 
 if there is an edge $e$ between nodes $u$ and $v$, then $adj(u, e) = v$.}
 \tcc{
 Global variable \pred{ResultPaths} contains all the resulted paths 
 }
 
 \BlankLine 
 \BlankLine
 
 \Fn(\tcc* {program starts here}){\FMain {$G, A$}}{
	$root$ = getRoot($G$)\;
	Mark $root$ as \pred{visited} \;
	\ForEach{edge $e$ starting at $root$}{
		Create a new path $P$ and add $(root, e)$ to $P$ \;
		$v$ = $adj(root, e)$ \;
		\FScan{$v, P, A$} \;
	}
	\If{\pred{ResultPaths} is not empty}{
		\KwRet \pred{ResultPaths}
	}
 }
 
 \BlankLine
  \BlankLine
  
 \Fn(\tcc*{search continue from $v$}){\FScan {$v, P, A$}}{
 	$base\_case$ = \pred{false} \;
 	\If(\tcc*[h]{reached a cycle}){$v$ is already \pred{visited}}{
 		$base\_case$ = \pred{true} \;
 	}
 	\ElseIf(\tcc*[h]{has no child}){$v$ is a leaf node}{
 		$base\_case$ = \pred{true} \;
 		Add $(v, \bot)$ to $P$ \;
 	}
 	\If{$base\_case$ is \pred{true}}{
 		\If{$P$ contains any edge with $A$}{
 			Add $P$ to \pred{ResultPaths} \;
 		}
 	}
 	\Else{
 		Mark $v$ as \pred{visited} \;
 		\ForEach{edge $e$ starting at $v$}{
 			$v'$ = $adj(v, e)$ \;
 			$P'$ = $copy(P)$ \;
 			Add $(v', e)$ to $P'$ \;
 			\FScan{$v', P', A$}
 		}
 		Mark $v$ as \pred{unvisited} \;
 	}
 	\KwRet \tcc*{void}
 }

% \Fn(\tcc*[h]{search continue from $v$}){\FScan {$v, P, A$}}{
% Queue $W_e \gets \emptyset$; FSM $M \gets \emptyset$\;
% Create initial program state $e_0$\;
%% \tcp{$q_0$ is the initial protocol FSM state}
% $q_0\gets\pred{ExtractFsmState}(e_0);$~~~$//q_0:$ initial protocol state\\
% $W_e.\pred{enqueue}(e_0);$\\
% $M.Q\gets \{q_0\};$ ~~~$//M.Q:$ set of states\\
% $M.q_I\gets q_0;$ ~~~~~~$//M.q_I:$ initial state\\
% $M.R\gets \emptyset;$ ~~~~~~~~$//M.R:$ set of transitions\\
% Mark state $q_0$ as old\;
% \While{$W_e \neq\emptyset$}{
%  $e_i \gets W_e.\pred{dequeue}()$\;
%  $q_i \gets \pred{ExtractFsmState}(e_i)$\;
%  \ForEach{Event $\tau\in \pred{EventList}$}{
%    $S_q\gets \pred{SymbolicExecution}(S, C, N, e_i,\tau)$\;
%    \ForEach{$\langle e_j, c, a\rangle\in S_q$}{
%        $q_j\gets \pred{ExtractFsmState}(e_j)$\;
%        \If{$q_j$ is not old}{
%         $W_e.\pred{enqueue}(e_j)$\;
%         $M.Q\gets M.Q\cup \{q_j\}$\;
%         Mark state $q_j$ as old \;
%        }
%        \If{Transition $\langle q_i, \tau, c, a, q_j\rangle$ is not old}{
%           $M.R\gets M.R\cup \{\langle q_i, \tau, c, a, q_j\rangle\}$\;
%           Mark transition $\langle q_i, \tau, c, a, q_j\rangle$ as old \;
%        }
%    }
%  }
% }
% \Return $M$
% }
 \caption{Find Vulnerable Paths\label{algorithm:modelsearch}} 
\end{algorithm}